Price of Anarchy for Mean Field Games

### 2018-08-02 PoA.tex
condensing Lemma 1

	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the linear first-order differential equation:
	\begin{equation*}
		\left({u}^{r \to \infty}_t\right)' - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
	\end{equation*}
	Then we have:
	\begin{equation*}
	u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u}.
	\end{equation*}
	It is easy to show directly from their explicit solutions that for every time $t\in [0,T]$, $$\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t, \quad \text{and thus,} \quad \lim_{r \to \infty}B^ru^r_t=0.$$

@@

	As noted in the proof of Proposition \ref{prop:b2_to_infty}, for $t\in[0,T)$, we have:
	$$\lim_{b_2 \to \infty}b_2\eta^{b_2}_t=(r + \bar{r}) c_{\delta_{\eta}^{b_2 \to \infty}}=\sqrt{(r+\bar{r})(q+\bar{q})} =: c_\eta.$$
	And thus, there exists $b_2^{*,1}$ such that for $b_2 \geq b_2^{*,1}$, we have

@@

	Since $\lim_{b_2 \to \infty} B^\eta (D^\eta)^2+2A^\eta D^\eta-C^\eta=\infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) there exists $b_2^{*,3}$ such that for $b_2 \geq b_2^{*,3}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing. Since for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing and continuous, by the intermediate value theorem, there exists a $t^*_{b_2}\in[0,T]$ such that:
	$$b_2 \eta^{b_2}_{t^*_{b_2}} =c_\eta+1, \quad \text{and} \quad b_2 \eta^{b_2}_t \leq c_\eta+1,\ \forall t\leq t^*_{b_2}.$$
	Thus for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$, we have:
	1=b_2\eta^{b_2}_{t^*_{b_2}}-c_\eta&=\frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}+\left(-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} \right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} +\left(\frac{\delta^{+,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}}\right) e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}}-c_\eta,

@@

	1=\frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}-\frac{D^\eta}{r+\bar{r}}c_\eta +\frac{\delta^{-,b_2}_\eta}{b_2^2}c_\eta+\left(-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} -\frac{\delta^{+,b_2}_\eta}{b_2^2}c_\eta +\frac{D^\eta}{r+\bar{r}}c_\eta\right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} +\left(\frac{\delta^{+,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}}\right) e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}},

@@

@@

	\frac{D^\eta}{r+\bar{r}}-&\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \\
	&= \left(-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} -\frac{\delta^{+,b_2}_\eta}{b_2^2}c_\eta +\frac{D^\eta}{r+\bar{r}}c_\eta -\frac{\delta^{+,b_2}_\eta}{b_2^2} +\frac{D^\eta}{r+\bar{r}} \right) e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})} \\
	&\leq  \left(-D^\eta\frac{\delta^{-,b_2}_\eta }{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right) e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}.

@@

	It is easy to derive the following limits:
	$$\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2^2}=\lim_{b_2 \to \infty}\frac{C^\eta}{b_2}=\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}=\lim_{b_2 \to \infty}\left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right) =0.$$
	Therefore, there exists $b_2^{*,4}$ such that for $b_2 \geq b_2^{*,4}$, we have:
	$$\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \leq \frac{D^\eta}{2(r+\bar{r})},$$

@@

	$$\frac{D^\eta}{2(r+\bar{r})}\leq \left(-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right) e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}, $$
	$$e^{\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}\leq -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) , $$
	$$\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})\leq \ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right) , $$

@@

	Finally, for $b_2 \geq b_2^{*,l}$, we have:

@@

	\int_0^T b_2 \eta^{b_2}_t dt&=\int_0^{t^*_{b_2}} b_2 \eta^{b_2}_t dt+\int_{t^*_{b_2}}^T b_2 \eta^{b_2}_t dt \\
	&\leq t^*_{b_2}(c_\eta+1)+b_2 (T-t^*_{b_2})D^\eta\\
	&\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left( 5c_\eta+2 \right)=:M^l.	

>>>>

	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the linear first-order differential equation:
	\begin{equation*}
		\left({u}^{r \to \infty}_t\right)' - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
	\end{equation*}
	Then we have:
	\begin{equation*}
	u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u}.
	\end{equation*}
	It is easy to show directly from their explicit solutions (see equation (\ref{eq:riccati_ut_sol})) that for every time $t\in [0,T]$, $$\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t, \quad \text{and thus,} \quad \lim_{r \to \infty}B^ru^r_t=0.$$

@@

	Since $\lim_{b_2 \to \infty}b_2\eta^{b_2}_t= c_\eta,$ there exists $b_2^{*,1}$ such that for $b_2 \geq b_2^{*,1}$, we have

@@

	Let $b_2^{*,3}$ such that for $b_2 \geq b_2^{*,3}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing. Since for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing and continuous, by the intermediate value theorem, there exists a $t^*_{b_2}\in[0,T]$ such that
	$b_2 \eta^{b_2}_{t^*_{b_2}} =c_\eta+1$, and $b_2 \eta^{b_2}_t \leq c_\eta+1$, for all $t\leq t^*_{b_2}.$
	From an analogous equation to (\ref{eq:riccati_ut_sol}) for $\eta^{b_2}_{t^*_{b_2}}$, we have for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$:

@@

	1=b_2\eta^{b_2}_{t^*_{b_2}}-c_\eta\leq \frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}-\frac{D^\eta}{r+\bar{r}}c_\eta +\frac{\delta^{-,b_2}_\eta}{b_2^2}c_\eta+\left(-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} +\frac{D^\eta}{r+\bar{r}}c_\eta\right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}} e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}},

@@

	After rearranging terms:

@@

	\frac{D^\eta}{r+\bar{r}}-\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}(1+c_\eta)+\frac{C^\eta}{b_2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right)\right]\\
	\leq  \left(-D^\eta\frac{\delta^{-,b_2}_\eta }{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right) e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}.

@@

	Since we have
	$\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2^2}=\lim_{b_2 \to \infty}\frac{C^\eta}{b_2}=\lim_{b_2 \to \infty}\left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right) =0,$ there exists $b_2^{*,4}$ such that for $b_2 \geq b_2^{*,4}$,
	$\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}(1+c_\eta)+\frac{C^\eta}{b_2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \leq \frac{D^\eta}{2(r+\bar{r})},$

@@

	$$\frac{D^\eta}{2(r+\bar{r})}\leq \left(-D^\eta\frac{\delta^{-,b_2}_\eta }{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right) e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}.$$
	After rearranging terms:

@@

	Finally, for $b_2 \geq b_2^{*,l}$:

@@

	\int_0^T b_2 \eta^{b_2}_t dt=\int_0^{t^*_{b_2}} b_2 \eta^{b_2}_t dt+\int_{t^*_{b_2}}^T b_2 \eta^{b_2}_t dt \leq t^*_{b_2}(c_\eta+1)+b_2 (T-t^*_{b_2})D^\eta \\
	\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left( 5c_\eta+2 \right)=:M^l.
